\textls[-0]{\thetitle}

### 2023-03-05 metatheory-condensed.tex
Add Caption.

We illustrate one concrete example of a "tm" with only two constructors, 
also as a review for how W-type encodes a given inductive type. The key insight 
is for a pair $(\wsigproj{i}{1}{\wsig}, \wsigproj{i}{2}{\wsig})$, the non-recursive
part of the given constructor stores in $\wsigproj{i}{1}{\wsig}$ and the ``arity'' of the 
recursive part stores in $\wsigproj{i}{2}{\wsig}$. For example, $"app" : ("tm" \to "tm" \to "tm")$ 
$\cong ((\bbtwo \to "tm") \to "tm")$, saying the ``arity'' of the recursive part is $\bbtwo$ 
(or boolean type, as a type with two elements). Similarly, the ``arity'' of recursive part of "unit" is 0. 
Both constructors don't store other information thus $\bbone$. We hightlight $\tau$ as the 
signature of our "tm" and showcase the meta-theoretic encoding of "unit" and "app~unit~unit". $"elim-"\bbzero$ indicates the elimination of the bottom type $\bbzero$ in the context. The key expressiveness of W-types comes from the ``arity'', as it encodes the case when recursive structure stores as the output of a function, mirroring the strict-positivity of Inductive type.

\begin{figure}
  \begin{tabular}{
    >{\columncolor[HTML]{C0C0C0}}l lcl}
    \hline
    \multicolumn{1}{|l}{\cellcolor[HTML]{C0C0C0}surface syntax} &
      \multicolumn{1}{l|}{Equivalent Type} &
      \multicolumn{1}{l}{} &
      \multicolumn{1}{l|}{} \\
    \multicolumn{1}{|l}{\cellcolor[HTML]{C0C0C0}\lsti!| unit : tm!} &
      \multicolumn{1}{l|}{$\bbone \times (\bbzero \to tm) \to tm$} &
      $\tau'$ &
      \multicolumn{1}{l|}{$\coloneqq\WSigAdd{\WSigEmp}{\bbone}{\bbzero}$} \\
    \multicolumn{1}{|l}{\cellcolor[HTML]{C0C0C0}\lsti!| app  : tm -> tm -> tm!} &
      \multicolumn{1}{l|}{$\bbone \times (\bbtwo \to tm) \to tm$} &
      $\tau$ &
      \multicolumn{1}{l|}{\cellcolor[HTML]{FFFFC7}$\coloneqq\WSigAdd{\tau'}{\bbone}{\bbtwo}$} \\ \hline
    \multicolumn{1}{c}{\cellcolor[HTML]{C0C0C0}\lsti!unit!} &
      $\coloneqq \Wsup{1}{\tau}{\unit}{"elim-"\bbzero}$ &
      \cellcolor[HTML]{C0C0C0}\lsti!app unit unit! &
      $\coloneqq\Wsup{0}{\tau}{\unit}{"unit"}$
    \end{tabular}
\end{figure}

>>>>

\begin{figure}
  \begin{tabular}{
    >{\columncolor[HTML]{C0C0C0}}l lcl}
    \hline
    \multicolumn{1}{|l}{\cellcolor[HTML]{C0C0C0}surface syntax} &
      \multicolumn{1}{l|}{Equivalent Type} &
      \multicolumn{1}{l}{} &
      \multicolumn{1}{l|}{} \\
    \multicolumn{1}{|l}{\cellcolor[HTML]{C0C0C0}\lsti!| unit : tm!} &
      \multicolumn{1}{l|}{$\bbone \times (\bbzero \to tm) \to tm$} &
      $\tau'$ &
      \multicolumn{1}{l|}{$\coloneqq\WSigAdd{\WSigEmp}{\bbone}{\bbzero}$} \\
    \multicolumn{1}{|l}{\cellcolor[HTML]{C0C0C0}\lsti!| app  : tm -> tm -> tm!} &
      \multicolumn{1}{l|}{$\bbone \times (\bbtwo \to tm) \to tm$} &
      $\tau$ &
      \multicolumn{1}{l|}{\cellcolor[HTML]{FFFFC7}$\coloneqq\WSigAdd{\tau'}{\bbone}{\bbtwo}$} \\ \hline
    \multicolumn{1}{c}{\cellcolor[HTML]{C0C0C0}\lsti!unit!} &
      $\coloneqq \Wsup{1}{\tau}{\unit}{"elim-"\bbzero}$ &
      \cellcolor[HTML]{C0C0C0}\lsti!app unit unit! &
      $\coloneqq\Wsup{0}{\tau}{\unit}{"unit"}$
    \end{tabular}
  \caption{W-type encoding of "tm \{unit, app\}"}
  \label{fig:Wtype-example}
\end{figure}

We illustrate one concrete example in \cref{fig:Wtype-example} of a "tm" with only two constructors, 
also as a review for how W-type encodes a given inductive type. The key insight 
is for a pair $(\wsigproj{i}{1}{\wsig}, \wsigproj{i}{2}{\wsig})$, the non-recursive
part of the given constructor stores in $\wsigproj{i}{1}{\wsig}$ and the ``arity'' of the 
recursive part stores in $\wsigproj{i}{2}{\wsig}$. For example, $"app" : ("tm" \to "tm" \to "tm")$ 
$\cong ((\bbtwo \to "tm") \to "tm")$, saying the ``arity'' of the recursive part is $\bbtwo$ 
(or boolean type, as a type with two elements). Similarly, the ``arity'' of recursive part of "unit" is 0. 
Both constructors don't store other information thus $\bbone$. We hightlight $\tau$ as the 
signature of our "tm" and showcase the meta-theoretic encoding of "unit" and "app~unit~unit". $"elim-"\bbzero$ indicates the elimination of the bottom type $\bbzero$ in the context. The expressiveness of W-types comes from the ``arity'', as it encodes the case when recursive structure stores as the output of a function, mirroring the strict-positivity of Inductive type.
